\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Bastian Haase} & Denver, CO \\
  Email : \href{mailto:bhaase2909@gmail.com}{bhaase2909@gmail.com} &  \href{github.com/bastihaase}{https://github.com/bastihaase} \\
 \href{https://www.linkedin.com/in/bastian-haase/}{https://www.linkedin.com/in/bastian-haase/} &  Mobile : +1-470-249-4020 
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{\textbf{Languages}{: Python, Scala, Java, SQL}}
    \item{\textbf{Technologies}{: AWS, Spark, Kafka, PostgreSQL, MySQL, Django, Flask, Airflow, Terraform, Docker}}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Director of Engineering}{San Francisco, CA}
      {Insight Data}{July 2018 -- Present}
      \resumeItemListStart
        \resumeItem{Director of Engineering, August 2020 -- Present}{}
        \resumeItem{Head of Engineering, August 2019 -- August 2020}{}
        \resumeItem{Engineering Lead, February 2019 -- August 2019}{}
        \resumeItem{Data Engineer/Program Director, July 2018 -- February 2019}{}
        \resumeItem{Data Engineering Fellow, April 2019 -- July 2018}{}
        \begin{itemize}
        \item Managed and grew a team offering a Fellowship program for ~200 Fellows, that transitioned from academia, SWE and data analytics into Data Engineering, Data Science, DevOps and Machine Learning Engineering.
        \item Analyzed historical Fellow placement and interview data and held regular product market fit retrospectives with team members to improve placement rates and inform focus of upcoming sprints.
        \item Managed Data Engineering and DevOps Engineering Fellows' projects building end-to-end Data platforms using open source technologies such as Spark, Kafka, Airflow, Cassandra, Docker, Kubernetes and Terraform.
        \item Provided technical mentorship to Fellows by developing and delivering workshops on System Design, SQL, Data Structures, Data Modeling and Docker.
        \item Supported Fellows in building infrastructure on AWS by providing instructions and code in Terraform, Docker and Ansible.
        \item Enabled data-driven interview preparation by building an interview tracking system capturing interview progress of hundreds of Fellows in real time on AWS using AWS Lambda, PostgreSQL and Flask.
        \item Added support for common Array functions to SparkSQL by working on Spark's source code using Scala and Java and \href{https://blog.insightdatascience.com/a-journey-through-spark-5d67b4af4b24}{published a blog} as a starting point to work on SparkSQL/open source.
        \end{itemize}
     \resumeItemListEnd



      \resumeSubheading{Ph.D Researcher}{Atlanta, GA}{Emory University}{August 2013 -- April 2018}
      \resumeItemListStart
        \resumeItem{Research in Algebraic Geometry}
          {Proved novel results in the theory of rational points by extending patching techniques and local-global principles in algebraic geometry.}
        \resumeItem{Instructor}
                   {Taught Calculus 1 and 2 to over 130 students and led weekly meetings for underperforming students to discuss study habits and best practices. All students participating
                   in the meetings passed the class with >90\% improving by at least one letter grade.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Emory University}{Atlanta, GA}
      {Ph.D in Mathematics}{Aug. 2013 -- Apr. 2018}
    \resumeSubheading
      {RWTH Aachen University}{Aachen, Germany}
      {Bachelor of Science in Mathematics;  Minor in CS}{Aug. 2010 -- July. 2013}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
